
In the final conclusions of this project, an overview must be done in order to gather the main conclusions about all the work that was developed. 

The main goal of the project was achieved, i.e, the use of the framework \textit{EL} to model a DBT and generate a final configurable system which has well defined interfaces between its components was done with success. It was proved that the \textit{EL} language, developed in Embedded Systems course, is well prepared to model a specific domains given its characteristics inherit from the SCA specification, used to describe software systems.

With this work, there was an improved of the modeling skills of the group and another advantage relies in the study of a dynamic binary translator, an embedded system represented by concepts of architectures and binary translation procedures. 

About the DBT model, the group concludes that a good model was created representing all software blocks presented in the original code. Also, the code refactoring was a success, since the code was changed structurally to fit in the model, maintaining its base engine and functionalities. It was proved that the language allows the injection of new behaviors without altering the interfaces, and that brings a prove of concept about the framework developed.  

Despite the advantages, a major problem was encountered during the implementation process. This was related with the hardware approach that was tried to achieve. One of the goals of the group was to incorporate an hardware implementation in the system, also configurable by the user and respecting the interfaces defined, although, given the deadline of the project, it was not possible to achieve the port of the system into another board.

As future perspectives, several things were though by the group to improve the work developed. The first one is related with the model of the DBT. More configurable points might be identified as well as new implementation should be tried in order to prove the concept of changing the behavior of the components respecting the same interfaces. The second one is related with the hardware implementation that were made but not used. If the port was achieved, new elaboration files should be created for each implementation. At last, another thing not implemented was a GUI for the application, since it can bring facilities in the configuration of the model. 